---
title: "Daniel Montoya Portfolio"
author: "Daniel Montoya"
date: "10/14/2021"
output: html_document: toc: true toc_depth: 3 toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Downcute


Displaying multiple vector layers on the same map
Calculating and displaying relationships among point and polygon layers based on distance
Aggregating point data to a layer of polygons
Calculating and displaying accessibility, based on travel time
Converting between raster layers and vector layers
Displaying raster data on a map
Georeferencing a raster image
Displaying data on an interactive map

Comments:

A1 Use Alpha
A2 Consistency
A3  You can create a table of contents automatically by replacing output: html_document at the top of your file with output: html_document: toc: true toc_depth: 3 toc_float: true
A45
A6


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
